Fivebranes

### 2022-05-17 fivebranes/index.tex
changes

\subsection{Local operators in a holomorphic theory}

@@

@@

Recall that the even part of $E(3|6)$ consists of two summands:
\[
\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
\]
Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_1,r_2\}$ as the fundamental $\lie{sl}(2)$ representation.

@@

Accordingly, the equivariant character we has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which acts by vector fields on $\C^{3}_{z}$.
  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_1,r_2\}$. 
  \item $q$ denotes a generator for the Cartan of an additional $\lie{gl}(1)$ which acts by dilations on $\C^3$. 
\end{itemize}
The weights are summarized in table \ref{tbl:weights1}.
Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.

@@

A remark comparing to Kac \cite{KR1}.

@@

@@

The specialization of this index in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
\]
which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.

@@

We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of fivebranes. Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}. Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$. Consider a stack of $N$ fivebranes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\pi : \R\times \C^{5}\to \C^{3}_{z_{i}}$ denote the canonical projection. The pushforward $\pi_{*} C^{*}(\cL)$ has the structure of a factorization algebra on $\C^{3}$

@@

The index we compute will have four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
  \item $q$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $r$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}

A convenient choice of choice of weights is as in the following table:

\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & 1 & 0 & -1 & 0 & 0 \\
  $t_{2}$ & 0 & 1 & -1 & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & -1 \\
  $q$ & -1 & -1 & -1 & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\end{center}

\begin{prop}
  The $\SU(3)\times \SU(2)\times U(1)$ character of the large $N$ local operators of the M5 brane theory is given by

  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}q+t_{1}t_{2}^{-1}q+t_{2}q+r^{-1}q^{-3/2}+rq^{-3/2} \\  - & t_{1}q^{-1}-t_{1}^{-1}t_{2}q^{-1}-t_{2}^{-1}q^{-1}-rq^{3/2}-r^{-1}q^{3/2}
          \end{aligned}\right)}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}\right ).\]
  \end{prop}

>>>>

\subsection{Local operators in a holomorphic-topological theory}

\begin{dfn} 
Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
\end{dfn}

Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
\[
\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
\]
where $L$ is a graded holomorphic vector bundle on $X$.

\begin{lem}
\label{lem:localops}
Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
Then, the Taylor expansion map
\[
\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
\]
induces a quasi-isomorphism of commutative dg algebras
\[
\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
\]
\end{lem}

@@

%\parsec[s:sugraops]
%
%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra. 
%
%On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
%\[
%\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
%\]
%The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
%\[
%\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
%\]
%which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$. 
%
%\begin{thm}[\cite{RSW}[Theorem 2.1]]
%The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
%\[
%j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
%\]
%Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
%\end{thm} 
%
%As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
%
%\begin{cor}
%\label{cor:sugraops}
%Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
%There is a quasi-isomorphism of commutative dg algebras
%\[
%\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
%\]
%\end{cor}

@@

Recall that the even part of $E(3|6)$ consists of two summands:
\[
\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
\]
Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.

@@

\begin{rmk}
In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
\cite{KacClass}.
\end{rmk}

The dimension of a Cartan subalgebra is four and accordingly, the equivariant character we study has four fugacities.
We choose these explicitly as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is generated by the vector fields
  \beqn
  z_1 \del_{z_1} - z_2 \del_{z_2} , \quad z_2 \del_{z_2} - z_3 \del_{z_3}
  \eeqn
  on~$\C^{3}_{z}$.
  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_+,r_-\}$. 
  \item $q$ denotes a generator for the Cartan of an additional $\lie{gl}(1)$ which acts by dilations on $\C^3$. 
\end{itemize}
The weights are summarized in table \ref{tbl:weights1}.
Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.

@@

A degeneration of this character was computed in \cite{KR1}. 
They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
\[
\frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3}
\]
which agrees with our direct analysis above.

@@

%\parsec[s:singleops]
%
%\begin{prop}
%Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
%There is a quasi-isomorphism of super commutative dg algebras 
%\[
%\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
%\]
%\end{prop}
%\begin{proof}
%This follows from Lemma \ref{lem:localops}.
%In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
%\beqn
%\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
%\eeqn
%and
%\beqn
%\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
%\eeqn
%The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
%The differential is zero on the odd summand.
%We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.
%
%From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
%\[
%(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
%\]
%That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
%\end{proof}

@@

The specialization of this index $t_1=t_2=r=1$ yields the single particle index
\[
\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
\]

The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
\]
which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.

@@

We now compute the equivariant character counting local operators of the holomorphic twist of the theory on a large number of fivebranes. 
Unlike the analysis above, we will the twisted holography proposal to compute this character.

Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}. Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$. Consider a stack of $N$ fivebranes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\pi : \R\times \C^{5}\to \C^{3}_{z_{i}}$ denote the canonical projection. The pushforward $\pi_{*} C^{*}(\cL)$ has the structure of a factorization algebra on $\C^{3}$

@@

We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra 
\[
\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)
\]
which embeds in the following way:
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect_0(\Hat{D}^3) \subset \Vect_0 (\Hat{D}^5)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ rotates the directions $\C_{w_1} \times \C_{w_2}$ transverse to the brane.
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by the vector field 
\beqn\label{vf1}
\sum_i z_i \frac{\del}{\del z_i} - \frac23 \sum_{j} w_j \frac{\del}{\del w_j} \in \Vect_0(\Hat{D}^5).
\eeqn
\end{itemize}

Correspondingly, the equivariant character thus has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ again denote generators for the Cartan of $\lie{sl}(3)$ acting by vector fields on $\C^{3}_{z}$.
  \item $r$ denotes a generators for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on the normal directions $\C_{w_1} \times \C_{w_2}$.
  \item $q$ denotes a generator for the Cartan of additional $\lie{gl}(1)$ generated by the divergence-free vector field \eqref{vf1}. 
\end{itemize}

This choice of weights is summarized in Table \ref{tbl:sugra}.

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & $-1$ \\
  $q$ & $-1$ & $-1$ & $-1$ & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity.}
\label{tbl:sugra}
\end{center}
\end{table}

\begin{prop}
  The character of local operators of the holomorphic twist of the theory on a large number of fivebranes is given by the following plethystic exponential

  \[ \rm PExp [f_{large N}(t_{1}, t_{2}, q, r)] \]

  where the single particle index is \[f_{large N}(t_{1}, t_{2}, q, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.\]
\end{prop}

The specialization $t_1=t_2=r=1$ yields the single particle index
\[
\frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
\]

\parsec 
The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{two}(t_1, 1, q, q^{1/2}) = \frac{q}{(1-q)^2}
\]

This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.

\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$ \surya{...}
